MSB104_assignment1

### 2023-10-05 MSB104_assignment1.qmd
Update 05.10.23

```{r}
merged_data <- merged_data %>%
  mutate(id_nuts2 = substr(Sub_regions,1,4))
#Gen Nuts 2 id
merged_temp <- merged_data %>%
group_by(id_nuts2, Year) %>%
mutate(gini_n2 = gini.wtd(GDP, Population)*100000) %>%
  ungroup()
```

```{r}
data <- data %>%
  mutate_(id_nuts3 = geo,
          id_nuts2 = substr(geo, 1,4),
          id_nuts0 = substr(geo, 1,2)
```

>>>>

```{r}
merged_data <- merged_data %>%
  mutate(id_nuts2 = substr(Sub_regions,1,4))
#Gen Nuts 2 id
merged_temp <- merged_data %>%
group_by(id_nuts2, Year) %>%
mutate(gini_n2 = gini.wtd(GDP, Population)*100000) %>%
ungroup() # to remove grouping
```

```{r}
merged_temp <- merged_temp %>%
  mutate(id_nuts2 = substr(Sub_regions, 1,4),
          id_nuts0 = substr(Sub_regions, 1,2))
```
